Microphysics and astrophysics inspired priors for neutron star mergers

### 2025-02-12 paper.tex
minor edits on methods section.

	In the neutron star binary case, we impose an upper bound on the binary tidal deformability from GW170817, requiring $\tilde{\Lambda} < 720$ under low-spin priors~\citep{Abbott2018a}. The tidal deformability is computed as
	\begin{equation} 
		\tilde{\Lambda}_{\rm NSNS} = \frac{16}{13} \frac{ (12M_2 + M_1) M_1^4 \Lambda_1 + (12M_1 + M_2) M_2^4 \Lambda_2}{(M_1 + M_2)^5}~,
	\end{equation}
	where $M_i$, $R_i$, and $\Lambda_i = \frac{2}{3} k_2 \left( R_i/M_i \right)^5$ ($i=1,2$) denote the component masses, radii, and tidal deformabilities, with $k_2$ being the second tidal Love number.
	EOSs violating $\tilde{\Lambda} < 720$ for a chirp mass $\mathcal{M}_{\rm chirp} = (M_1 M_2)^{3/5} (M_1+M_2)^{-1/5} = 1.186,M_\odot$ and mass ratio $q = M_2/M_1 > 0.73$ are discarded.

	In the mixed binary case, i.e., where one binary component is a neutron star and the other one a black hole, the formula for the binary tidal deformability simplifies, because black holes have zero tidal deformability $\Lambda_{\rm BH}=0$.
	The binary tidal deformability in this case becomes
	\begin{equation} 
		\tilde{\Lambda}_{\rm NSBH} = \frac{16}{13} \frac{ (12M_{\rm BH} + M_{\rm NS}) M_{\rm NS}^4 \Lambda_{\rm NS}}{(M_{\rm NS} + M_{\rm BH})^5}~,
	\end{equation}
	where $M_{\rm NS}$ and $\Lambda_{\rm NS}$ are the nuetron star mass and tidal defromability, respectively, and $M_{\rm BH}$ the black hole mass. The expressions for the chirp mass and mass ratio remain intact, with the understanding that $M_1=M_{\rm NS}$ and $M_2=M_{\rm BH}$. 
	%Applying these observational constraints reduces our initial set of $8 \times 10^6$ EOSs to approximately $10^6$ viable models, forming the basis for the results in the next section.

	%While an upper bound on $M_{\rm TOV}$ has been proposed ($M_{\rm TOV} \lesssim 2.16^{+0.17}{-0.15} M{\odot}$, see \citet{Rezzolla2017} and also \citet{Margalit2017, Ruiz2017, Shibata2019, Nathanail2021}), this estimate relies on model assumptions about the kilonova associated with GRB170817A from GW170817. Given these uncertainties, we do not impose this bound in our main analysis but explore its impact in Appendix~\ref{sec:appendix_a}.

>>>>

	In the neutron star binary case, the binary tidal deformability is computed as
	\begin{equation} 
		\tilde{\Lambda}_{\rm NSNS} = \frac{16}{13} \frac{ (12M_2 + M_1) M_1^4 \Lambda_1 + (12M_1 + M_2) M_2^4 \Lambda_2}{(M_1 + M_2)^5}~,
	\end{equation}
	where $M_i$, $R_i$, and $\Lambda_i = \frac{2}{3} k_2 \left( R_i/M_i \right)^5$ ($i=1,2$) denote the component masses, radii, and tidal deformabilities, with $k_2$ being the second tidal Love number.
	The chirp mass is given by $\mathcal{M}_{\rm chirp} = (M_1 M_2)^{3/5} (M_1+M_2)^{-1/5}$ and we in the following we will use the mass ratio defined as $q = M_2/M_1$.

	In the mixed binary case, i.e., where one binary component is a neutron star and the other one a black hole, the formula for the binary tidal deformability simplifies, because black holes have zero tidal deformability $\Lambda_{\rm BH}=0$.
	The binary tidal deformability in this case becomes
	\begin{equation} 
		\tilde{\Lambda}_{\rm NSBH} = \frac{16}{13} \frac{ (12M_{\rm BH} + M_{\rm NS}) M_{\rm NS}^4 \Lambda_{\rm NS}}{(M_{\rm NS} + M_{\rm BH})^5}~,
	\end{equation}
	where $M_{\rm NS}$ and $\Lambda_{\rm NS}$ are the nuetron star mass and tidal defromability, respectively, and $M_{\rm BH}$ the black hole mass. The expressions for the chirp mass and mass ratio remain intact, with the understanding that $M_1=M_{\rm NS}$ and $M_2=M_{\rm BH}$.
